---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# etd

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The data structure for potentially censored data in the survival package has served the community well. However, it was created in the mid 1980's for the S language. 

etd (Event Time Data) proposes a data structure that: 

- Is an R vctrs class (not a matrix)
- Has more obvious status values (descriptive letters instead of integer codes)
- Can easily accommodate different types of censoring. 

## Installation

You can install the development version of etd like so:

``` r
pak::pak("topepo/etd)
```

## Examples

Suppose we have data with complete event times as well as left_ and right censored data: 


```{r}
set.seed(1)
observed_times <- sort(rexp(5))
status <- c("left censored", rep("event", 3), "right censored")
```

With etd, the `event_time()` function takes the time values as is and uses status values of "e" (events), "l" (left censored), "r" (right censored), or "i" (interval censored). 

```{e}
library(etd)

etd_obj <- event_time(observed_times, substr(status, 1, 1))
etd_obj
is.matrix(etd_obj)

# Add to a data frame: 
etd_df <- data.frame(times = etd_obj)
etd_df
```

